---
title: "ProjectMain"
author: "Noah Nsangou"
date: "11/25/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(jsonlite)
library(stringdist)
library(caTools)
IMDB_movie_details <- stream_in(file("IMDB_movie_details.json"))
IMDB_reviews <- stream_in(file("IMDB_reviews.json"))
```


```{r}
head(IMDB_movie_details)
head(IMDB_reviews)
```

### Data Grooming

## Size reduction
```{r}
lite_movie_details <- na.omit(IMDB_movie_details[IMDB_movie_details$plot_synopsis != "",])[1:400,]
lite_movie_df <- merge(x = IMDB_reviews, y = lite_movie_details, by = "movie_id")

```



### PREDICTORS:

## Review Length
```{r}
review_length <- length(mySplit(IMDB_reviews$review_text))
```

## Rating
```{r}
lite_movie_details$rating <- as.double(lite_movie_details$rating)
lite_movie_df$rating.y <- as.double(lite_movie_df$rating.y)
lite_movie_df$rating.x <- as.double(lite_movie_df$rating.x)
```

## Mean Rating 

```{r}
temp_std = lite_movie_df %>% select(movie_id, rating.x) %>% group_by(movie_id) %>% summarise(std_rating = sd(rating.x))

lite_movie_df <- merge(x = lite_movie_df, y = temp_std, by = "movie_id", all.x = T)
lite_movie_df$z_score = 0
lite_movie_df$z_score = (lite_movie_df$rating.y - lite_movie_df$rating.x)*1.00/lite_movie_df$std_rating

head(lite_movie_df)
```


## Gemre

```{r}
#reduced the category to 1. Action 2. Thriller 3. Romance 4. Comedy 5. Fantasy

#create slots for the predictors
lite_movie_df['isAction'] = 0
lite_movie_df['isComedy'] = 0
lite_movie_df['isRomance'] = 0
lite_movie_df['isThriller'] = 0
lite_movie_df['isFantasy'] = 0

#for loop to add more categorical variables
for (i in 1:nrow(lite_movie_df)){
  
  if("Action" %in% lite_movie_df[[i,'genre']]){
    lite_movie_df[i,'isAction'] = 1  
  }

  if("Comedy" %in% lite_movie_df[[i,'genre']]){
    lite_movie_df[i,'isComedy'] = 1  
  }

  if("Romance" %in% lite_movie_df[[i,'genre']]){
    lite_movie_df[i,'isRomance'] = 1  
  }

  if("Thriller" %in% lite_movie_df[[i,'genre']]){
    lite_movie_df[i,'isThriller'] = 1  
  }

  if("Fantasy" %in% lite_movie_df[[i,'genre']]){
    lite_movie_df[i,'isFantasy'] = 1
  }
}

head(lite_movie_df)
```



##Review dates 

Join two dataset via movie_id


Took the difference between years because some dates are missing month, day variables.


```{r}
library(lubridate)

#turn string yr to integer
lite_movie_df["yr_review"] = strtoi(format(as.Date(lite_movie_df$review_date, format="%d %B %Y"), "%Y"))
lite_movie_df["yr_release"] = strtoi(substr(lite_movie_df$"release_date",1,4))

#store the result in time elapsed
lite_movie_df["time_elapsed_yr"] = lite_movie_df["yr_review"] -(lite_movie_df["yr_release"])

head(lite_movie_df)
```

# 3. User behavior (predictor 3,4 ): total number of reviews, repeat offender

```{r}

#match("ur22570173",lite_movie_df$user_id)

library(dplyr)
lite_movie_df["N"] = 1

temp = lite_movie_df %>% select(user_id, is_spoiler, N) %>% group_by(user_id) %>% summarise(repeat_offender = max(is_spoiler), num_review = sum(N))

## join with the existing column (added columns: repeat offender, number of reviews in the past)
lite_movie_df = merge(x = lite_movie_df, y = temp, by = "user_id", all.x =T)

head(lite_movie_df)
```


# 4. contains special character (predictor 5)

```{r}
library(stringr)

#number of special chars
lite_movie_df["special_char"] = str_count(lite_movie_df$review_text,"[^a-zA-Z0-9^ ^,^.]")
head(lite_movie_df)
```


# 5. correct grammar checker (predictor 6) -- takes a long time
## probably takes into account

```{r}
library(hunspell)

hunspell_list = function(x){
  x = length(hunspell(x)[[1]])
  x
}

Error_Count= apply(lite_movie_df["review_text"], c(1,2), hunspell_list)

```


# 6. Run time (predictor 7) -- convert back to minute

```{r}

extract_time = function(x){
  x = strsplit(x, "h |min")[[1]]
  
  if(length(x) > 1){
    x = strtoi(x[1])*60 + strtoi(x[2])  
  }
  else{
    x = strtoi(x[1])
  }
  x
}

# use the apply function to extract time 
temp = apply(lite_movie_df["duration"], c(1,2), extract_time)
lite_movie_df["duration_min"] = c(temp)
head(lite_movie_df)
```

## Response Variable Boolean to Binary

```{r}
lite_movie_df$is_spoiler <- as.numeric(lite_movie_df$is_spoiler)
head(lite_movie_df)
```


```{r}
cols = c(colnames(lite_movie_df))
write.table(lite_movie_df[,!cols %in% c("review_text","review_summary","plot_summary","plot_synopsis","genre")],
            file = "lite_movie_df.tsv", sep = "\t", row.names = F)
```




### Train / Test Split
```{r}
# Test = False
#details_partition_vec <- sample.split(IMDB_movie_details)
partition_vec <- sample.split(IMDB_reviews$review_text, SplitRatio = 2/3)
review_train <- IMDB_reviews[review_partition_vec,]

```






