---
title: "ProjectAnalysis"
output: html_document
---


```{r}
library(jsonlite)
library(stringdist)
library(caTools)
df_lite = read.delim("lite_movie_df_2.tsv")
df_reviews = stream_in(file("IMDB_reviews.json"))
head(df_lite)
```


## Part 1: Sentiment analysis

```{r}
library(tidytext)
library(stringr)
library(textdata)
library(dplyr)

#join the most updated version of df with the review_text
df_lite_review <- merge(x = df_lite, y = df_reviews[,c("movie_id","user_id","review_text")], by = c("movie_id", "user_id"))

#unnest all review words
review_words = df_lite_review %>% unnest_tokens(word, input = review_text)

#count the number of words
wordcounts = review_words %>% group_by(movie_id, user_id) %>% summarize(words = n())
```



```{r}
#extract negative & positive & surprise words
bingnegative <- get_sentiments("bing") %>% filter(sentiment == "negative")
bingpositive <- get_sentiments("bing") %>% filter(sentiment == "positive")
nrc_surprise <- get_sentiments("nrc") %>% filter(sentiment == "surprise")

#extract sentiment scores
sentiment_df_neg <- review_words %>%
  semi_join(bingnegative) %>%
  group_by(movie_id, user_id) %>%
  summarize(negativewords = n()) %>%
  left_join(wordcounts, by = c("movie_id","user_id")) %>%
  mutate(negratio = negativewords/words) %>% ungroup()

sentiment_df_pos <- review_words %>%
  semi_join(bingpositive) %>%
  group_by(movie_id, user_id) %>%
  summarize(positivewords = n()) %>%
  left_join(wordcounts, by = c("movie_id","user_id")) %>%
  mutate(posratio = positivewords/words) %>% ungroup()

sentiment_df_surprise <- review_words %>%
  semi_join(nrc_surprise) %>%
  group_by(movie_id, user_id) %>%
  summarize(surprisewords = n()) %>%
  left_join(wordcounts, by = c("movie_id","user_id")) %>%
  mutate(surpriseratio = surprisewords/words) %>% ungroup()

```

```{r}
tail(sentiment_df_surprise)
tail(sentiment_df_neg)
tail(sentiment_df_surprise)
```


```{r}

#join back to the original df_lite
df_lite = merge(x = df_lite, y = sentiment_df_neg[,c("movie_id","user_id","negratio")], by = c("movie_id", "user_id"),
      all.x = T)
df_lite = merge(x = df_lite, y = sentiment_df_pos[,c("movie_id","user_id","posratio")], by = c("movie_id", "user_id"),
      all.x = T)
df_lite = merge(x = df_lite, y = sentiment_df_surprise[,c("movie_id","user_id","surpriseratio")], by = c("movie_id", "user_id"),
      all.x = T)
```

## change the repeat_offender flag


```{r}
temp = df_lite %>% select(user_id, is_spoiler, N) %>% group_by(user_id) %>% summarise(repeat_offender = (sum(is_spoiler) > 1), num_review = sum(N))


#update the repeat_offender flag
df_fin = merge(x = df_lite[,!names(df_lite) %in% c("repeat_offender","num_review")], y = temp, by = "user_id", all.x =T)

```

## write to a new df
```{r}
write.table(df_fin, file = "lite_movie_df_update.tsv", sep = "\t", row.names = F)
```


## wordcloud image for spoiler / nonspoiler

```{r}
library(wordcloud)
#overall words included in the review_words
review_words %>% anti_join(stop_words) %>% count(word) %>% with(wordcloud(word, n, max.words = 100))

#words included in the is_spoiler == 0
review_words[which(review_words$is_spoiler == 0),] %>% anti_join(stop_words) %>% count(word) %>% with(wordcloud(word, n, max.words = 100))

#words included in the is_spoiler == 1
review_words[which(review_words$is_spoiler == 1),] %>% anti_join(stop_words) %>% count(word) %>% with(wordcloud(word, n, max.words = 100))
```




## Part 2: Exploratory Data Analysis


```{r}
df_fin = read.delim("lite_movie_df_update.tsv")
head(df_fin)
```

### unbalanced
```{r}
library(ggplot2)
group_0 = df_fin[which(df_fin$is_spoiler == 0),]
group_1 = df_fin[which(df_fin$is_spoiler == 1),]

barplot(c(nrow(group_0),nrow(group_1)), col="orange",
        names.arg=c("True","False"),
        xlab = "is_spoiler",
        ylab = "frequency",
        main = "Ratio of Response Variable (is_spoiler = T/F)",
        cex.main = 1.2)
```



### genre spoiler/not spoiler ratio
```{r}
par(mfrow=c(1,4))

g1 = df_fin[which(df_fin$isAction == 1),]
g2 = df_fin[which(df_fin$isComedy == 1),]
g3 = df_fin[which(df_fin$isRomance == 1),]
g4 = df_fin[which(df_fin$isThriller == 1),]
g5 = df_fin[which(df_fin$isFantasy == 1),]

check_ratio = function(x){
  group0 = x[which(x$is_spoiler == 0),]
  group1 = x[which(x$is_spoiler == 1),]
  c(nrow(group0),nrow(group1))
}

df_ratio = data.frame(action_ratio = check_ratio(g1), 
           comedy_ratio = check_ratio(g2),
           romance_ratio = check_ratio(g3),
           thriller_ratio = check_ratio(g4),
           fantasy_ratio = check_ratio(g5)
           )
```



```{r}
barplot(as.matrix(df_ratio),beside = T,
        xlab = "is_spoiler",
        ylab = "frequency",
        main = "Ratio of Response Variable (is_spoiler = T/F)",
       col=c("#7BD9A5","#D97BAA"), #names.arg=c("True","False"),
      cex.main = 1.2)
legend("topright",
       c("is_spoiler = False","is_spoiler = True"),
       fill = c("#7BD9A5","#D97BAA")
       )
```


### repeat_offender ratio


```{r}
par(mfrow=c(1,2))

SpoilRepeatT = nrow(subset(df_fin, is_spoiler ==1 & repeat_offender==TRUE))
SpoilRepeatF = nrow(subset(df_fin, is_spoiler ==1 & repeat_offender==FALSE))

NSpoilRepeatT = nrow(subset(df_fin, is_spoiler ==0 & repeat_offender==TRUE))
NSpoilRepeatF = nrow(subset(df_fin, is_spoiler ==0 & repeat_offender==FALSE))


barplot(c(SpoilRepeatT, SpoilRepeatF),
        xlab = "Repeat offender",
        ylab = "frequency",
        ylim = c(0,100000),
        main = "Ratio of Repeat Offender for is_spoiler = TRUE",
       col=c("#7BD9A5","#D97BAA"), names.arg=c("True","False"),
      cex.main = 0.8)

barplot(c(NSpoilRepeatT, NSpoilRepeatF),
        ylim = c(0,100000),
        xlab = "Repeat offender",
        ylab = "frequency",
        main = "Ratio of Repeat Offender for is_spoiler = FALSE",
       col=c("#7BD9A5","#D97BAA"), names.arg=c("True","False"),
      cex.main = 0.8)
```


```{r}
head(df_fin)
```


### Distribution time_elapsed_yr, yr_release, yr_review, rating.x, duration,  

```{r}
par(mfrow=c(3,4))

#time passed
with(df_fin,hist(time_elapsed_yr,col="lightblue",main="",nclass=10,cex=2.2,ps=30,cex.sub=2))
with(df_fin,hist(yr_release,col="lightblue",main="",nclass=10,cex=2.2,ps=30,cex.sub=2))
with(df_fin,hist(yr_review,col="lightblue",main="",nclass=10,cex=2.2,ps=30,cex.sub=2))

#num reviews
with(df_fin,hist(num_review,col="lightblue",main="",nclass=10,cex=1.2))

#sentiments
with(df_fin,hist(surpriseratio.x,col="lightblue",main="",nclass=10,cex=1.2))
with(df_fin,hist(posratio,col="lightblue",main="",nclass=10,cex=1.2))
with(df_fin,hist(negratio,col="lightblue",main="",nclass=10,cex=1.2))

#number of matches
with(df_fin,hist(SynopsisReviewOverlap,col="lightblue",main="",nclass=10,cex=1.2))

#rating (individual)
with(df_fin,hist(rating.x,col="lightblue",main="",nclass=10,cex=1.2))

#duration
with(df_fin,hist(duration_min,col="lightblue",main="",nclass=10,cex=1.2))

```



### correlation between is_spoiler and other numerical variables

1. time_elapsed 2. yr_release 3. yr_review 4. rating.x (individual) 5. duration (min) 
6. repeat_offender 7. num_review 8. special character 9. z_score 10. review_length 11. synopsis review
12. sentiment ratios 


### Running logistic regression


The most basic model:

```{r}
lm.basic = glm(is_spoiler ~ rating.x + isAction + isComedy + isRomance + isThriller + 
      isFantasy + yr_review + yr_release + time_elapsed_yr + special_char + 
      duration_min + z_score + review_length + SynopsisReviewOverlap + negratio +
      posratio + surpriseratio.x + repeat_offender + num_review, 
      data = df_fin, family = "binomial")
summary(basic_model)
```


**HERE**


### Full model (with iteraction terms), AIC, BIC

```{r}
lm.step = step(lm.basic, trace = 0)
summary(lm.step)
```




